\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
Reply comments.

An inheritance data\YZ{what is 'inheritance data'?} will be annotated with the type for the input family
and output family. There are three kinds of inheritance---extend,
override, and inherit. Extending corresponds to adding new fields,
overriding corresponds to modifying existent fields, and inheriting
corresponds to directly taking fields from the parent.
Thus, it is possible to consider inheritance as solely a data rather
than a functor, and this actually provides us the possibility to
\text{mix-in} inheritance data.

>>>>

An inheritance data\YZ{what is 'inheritance data'?}\EDJreply{It is just inheritance judgement, but before meta-theory is introduced, I can only say some "first-order data that represent the information of inheritance". I emphasize first order to distinguish from functor in ML community.} 
will be annotated with the type for the input family
and output family. There are three kinds of inheritance---extend,
override, and inherit. Extending corresponds to adding new fields,
overriding corresponds to modifying existent fields, and inheriting
corresponds to directly taking fields from the parent.
Thus, it is possible to consider inheritance as solely a data rather
than a functor, and this actually provides us the possibility to
\text{mix-in} inheritance data.
